---
name: Anna
surname: Quaglieri (PhD)
position: "Bioinformatics Data Scientist"
address: "Mass Dynamics"
email: "anna.quaglieri16@gmail.com"
twitter: annaquagli
github: annaquaglieri16
linkedin: anna-quaglieri-692501108
orcid: 0000-0002-3660-6990
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---


```{r setup, include=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
renv::restore()
#pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')

library(googlesheets4)

readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  #all <- read_sheet('https://docs.google.com/spreadsheets/d/1beQJHYgh9pp040y8m27ItCeENGCf4VD7Sv5k2ddBpDU/edit#gid=554957228', range = 1:6)
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

library(here)
library(dplyr)
library(vitae)
readExcelSheets(file.path(here(),"CV.xlsx"))
```



# Education

```{r}
education %>% 
  detailed_entries(what = institution,
                   when = year,
                   why=details, .protect = F)
```

# Employment

```{r}
employment %>% 
  detailed_entries(what = company,
                   when = year,
                   why = details, .protect = F)
```

# Leadership Roles

```{r}
leadership %>% 
  detailed_entries(when = year,
                   what = group,
                   why = details, .protect = F)
```


# Public speaking

```{r}
talks %>% 
  detailed_entries(what = group,
                   when = year,
                   why = details, .protect = FALSE)
```

\newpage
# Publications
\footnotesize

```{r publications} 
#bibliography_entries("pubs.bib", "Publications") 
``` 


- J. Bloom; **A. Quaglieri**; A. Triantafyllidis; P. Burton Ngov; G. Infusini; A. Webb (2021) "Mass Dynamics 1.0: A Streamlined, Web-Based Environment for Analyzing, Sharing, and Integrating Label-Free Data".  Journal of Proteome Research. DOI: 10.1021/acs.jproteome.1c00683 \href{10.1021/acs.jproteome.1c00683}{\faExternalLink}

- **A. Quaglieri**; C. Flensburg; T.P Speed; Ian J Majewski (2020). "Finding a suitable library size to call variants in RNA-Seq". BMC Bioinformatics 21, 553. DOI: https://doi.org/10.1186/s12859-020-03860-4 \href{https://doi.org/10.1186/s12859-020-03860-4}{\faExternalLink}

- **Anna Quaglieri** (2019) PhD Thesis: "Using transcriptomics to study relapse in acute myeloid leukaemia", Published at University of Melbourne \href{shorturl.at/drABC}{\faExternalLink}

- C. D. DiNardo; I. S. Tiong; **A. Quaglieri**; S. MacRaild; S. Loghavi; F. C. Brown; R. Thijssen; G. Pomilio; A. Ivey; J. M. Salmon et al. (2020) "Molecular Patterns of Response and Treatment Failure after Frontline Venetoclax Combinations in Older Patients with AML". Blood 135 (11): 791-801. DOI: 10.1182/blood.2019003988 \href{10.1182/blood.2019003988}{\faExternalLink}

- TS Scerri; **A. Quaglieri**, C. Cai; J JZernant; N. Matsunami; L. Baird; L. Scheppke; R. Bonelli; LA Yannuzzi; M. Friedlander; MacTel Project Consortium; C.A. Egan; M. Fruttiger; M. Leppert; R. Allikmets; M. Bahlo (2017) "Genome-wide analysis identifies common variants associated  with macular telangiectasia type 2" Nature Genetics 49(4):559-567. DOI: 10.1038/ng.3799 \href{10.1038/ng.3799}{\faExternalLink}

- A. Farioli; S. Mattioli; **A. Quaglieri**; S. Curti; F.S. Violante; D. Coggon (2014)  "Musculoskeletal pain in Europe: the role of personal, occupational, and social risk factors." Scandinavian Journal of Work, Environment & Health 40(1):36-46. DOI: 10.5271/sjweh.3381 \href{10.5271/sjweh.3381}{\faExternalLink}

# Public Outreach

```{r}
public_outreach %>%
  brief_entries(what = glue::glue("\\textbf{<what>}: <details>", .open = "<", .close = ">"),
                when = paste0(c(2017, 2018), "\\newline"), .protect = FALSE)
```


# Awards and scholarships

```{r}
awards %>%
  brief_entries(what = glue::glue("\\textbf{<what>}: <details>", .open = "<", .close = ">"),
                when = paste0(when, "\\newline"), .protect = FALSE)
```

