%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Anna}{Quaglieri (PhD)}

\position{Bioinformatics Data Scientist}
\address{Mass Dynamics}

\email{\href{mailto:anna.quaglieri16@gmail.com}{\nolinkurl{anna.quaglieri16@gmail.com}}}
\orcid{0000-0002-3660-6990}
\github{annaquaglieri16}
\linkedin{anna-quaglieri-692501108}
\twitter{annaquagli}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{PhD Student, WEHI Bioinformatics, Speed Lab}{}{}{Feb16-Sept19}{\begin{cvitems}
\item PhD thesis: "Using transcriptomics to study relapse in acute myeloid leukaemia" \href{http://hdl.handle.net/11343/234028}{\faExternalLink}. The research focused on building a statistical framework to improve the understanding of the relapse mechanisms in particular subtypes of Acute Myeloid Leukemia.
\end{cvitems}}
    \cventry{Master Degree in Statistics, Universities of Bologna and Melbourne}{}{}{Sep12-Jul14}{}\vspace{-4.0mm}
    \cventry{Master Thesis, WEHI Bioinformatics, Bahlo Lab}{}{}{Sep12-Jul14}{\begin{cvitems}
\item Title: “Genome-Wide association study in presence of relatedness – Application to an eye disorder”. Preparation and analysis of SNP-Chip data from patients with
a rare genetic eye disease, known as MacTel. Goal to perform a pilot GWAS for a larger study that was conducted for Scerri TS et al, 2017, Nature Genetics \href{https://www.nature.com/articles/ng.3799}{\faExternalLink}
\end{cvitems}}
    \cventry{Internship in Biostatistics, S.Orsola-Malpighi Hospital, Bologna}{}{}{Jul12-Sep12}{\begin{cvitems}
\item Part of Master degree. The work involved data collection, cleaning, statistical modeling and led to the publication Farioli A et al (2014) \href{https://www.sjweh.fi/show_abstract.php?abstract_id=3381}{\faExternalLink} which was awarded the ISICO Paper Prize in 2014
\end{cvitems}}
    \cventry{Undergraduate Degree in Statistics, Universities of Bologna and Glasgow}{}{}{Sep09-Jul12}{\begin{cvitems}
\item Title of Statistics Senior Honours project in Glasgow supervised by Professor Marian Scott (University of Glasgow): "Cancer in dogs and quality of life impact". Data analysed using generalised additive models and mixed
effect models for longitudinal data.
\end{cvitems}}
\end{cventries}

\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{Bioinformatics Data Scientist at Mass Dynamics, Melbourne}{}{}{May21-Current}{\begin{cvitems}
\item Guide Product team decisions with regards to statistical and bioinformatics techniques;
\item Support users with methods and platform consultation so that they can achieve their outcome;
\item Develop the scientific methods and sofwtare assets of the platform. Developed R Package MassExpression \href{https://github.com/MassDynamics/MassExpression}{\faExternalLink} to support processing of label-free quantitative data.
\item Participate and present at scientific conferences and contribute to scientific manuscript writing (Contributed to Bloom J et al (2021) \href{https://pubs.acs.org/doi/10.1021/acs.jproteome.1c00683}{\faExternalLink})
\end{cvitems}}
    \cventry{Data Scientist Consultant at Eliiza, Melbourne}{}{}{Nov19-May21}{\begin{cvitems}
\item Developed a Python workflow to pre-process and identify burnt areas from satellite images
\item Led the development of a Python library to automate information extraction from documents. Now this is a product of the company Thea \href{https://eliiza.com.au/product/thea-document-processing/}{\faExternalLink}.
\item Built classification models used and deployed into client’s production environment
\end{cvitems}}
    \cventry{Tutor in Stastics at University of Melbourne}{}{}{Mar18-May18}{\begin{cvitems}
\item “Critical thinking with data (UNIB10006)” and “Data and decision making (MAST90072)”
\end{cvitems}}
    \cventry{Bioinformatics Research Assistant, WEHI, Majewski Lab}{}{}{Oct2019-Jan2019}{\begin{cvitems}
\item Completion of PhD projects published in two papers: Courtney D Nardo et al (2020)\href{https://ashpublications.org/blood/article/135/11/791/430257/Molecular-patterns-of-response-and-treatment}{\faExternalLink} where I performed statistical analysis of the RNA-Seq data and Quaglieri et al, (2019), BMC Bioinformatics\href{https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03860-4}{\faExternalLink} where I was the first author and performed all the analyses.
\end{cvitems}}
    \cventry{Bioinformatics Research Assistant, WEHI, Speed and Bahlo Labs}{}{}{Sep13-Mar16}{\begin{cvitems}
\item Speed lab: Worked as the main statistician in epigenetics projects (Under publication) and collaborated in the creation of an R package for GC bias correction of ChIP-Seq data where the task was to upgrade existing R functions (unpublished work).
\end{cvitems}}
    \cventry{Bioinformatics Research Assistant, WEHI, Bahlo Labs}{}{}{Sep13-Mar16}{\begin{cvitems}
\item Bahlo lab: Statistician in the team which discovered the first genetic clues for Macular Telangiectasia Type 2 disease through Genome-Wide Association study (Bahlo lab) (Scerri TS et al 2017, Nature Genetics) \href{https://www.nature.com/articles/ng.3799}{\faExternalLink}.
\end{cvitems}}
\end{cventries}

\hypertarget{leadership-roles}{%
\section{Leadership Roles}\label{leadership-roles}}

\begin{cventries}
    \cventry{R-Ladies Melbourne (President and Co-organiser)}{}{}{Oct16-Ongoin}{\begin{cvitems}
\item The group (\href{www.meetup.com/R-Ladies-Melbourne/}{Meetup page: www.meetup.com/R-Ladies-Melbourne/}, founded in 2016, is the first R Programming community for women and supporters in Australia. President of the group in 2017/2018 where we organised 12 events (workshops, seminars and networking nights) doubling in members; defined the structure to become a not-for-profit association; provided funding for women to attend the useR! conference; gained a new sponsor Nous Group and renewed sponsorship from CSL. Helped running and organising events since 2016.
\end{cvitems}}
    \cventry{Parkville Toastmasters (VPM)}{}{}{2022-Ongoing}{\begin{cvitems}
\item As Vice President Membership (VPM) I'm in charge of running inductions with new members to intriduce them to the club and how Toastmasters work; setting up new members into the system; organising mentorship between new and established members.
\end{cvitems}}
    \cventry{Bioconductor Code of Conduct (Secretary)}{}{}{2021-Ongoing}{\begin{cvitems}
\item The CoC committee is responsible to file incidents and lead to a conflict resolution which will depend on the gravity of the incident. I share the same role as any other member in supporting conflict resolution and as secretary I set up meetings dates with committee members and organise minutes.
\end{cvitems}}
    \cventry{useR! Conferences organising committee}{}{}{2018/2019 Brisbane/Toulouse}{\begin{cvitems}
\item UseR! Is one of the most important annual international R conferences. Main task to review abstracts and scholarship applications. In Brisbane also organised the logistics of R-Ladies Melbourne travel scholarships to support national participants.
\end{cvitems}}
    \cventry{Workers Club Lions Australian Football Club (Treasurer and Captain)}{}{}{2017-2021}{\begin{cvitems}
\item Treasurer: The role involves looking after incoming funds to the club which come from selling merchandise at the Workers Club and fundraising events. Captain: On field captain of the football team.
\end{cvitems}}
    \cventry{Mentor at BrainSTEMM}{}{}{2018.0}{\begin{cvitems}
\item Co-mentored a group of four high school girls from Gippsland for a three months period. Students for exposed to what it means to do research in science; learnt coding and basic principles of statistics for the first time; presented their final work in an inspiring video and organised a coding day where they became coding instructors for their classmates.
\end{cvitems}}
\end{cventries}

\hypertarget{public-speaking}{%
\section{Public speaking}\label{public-speaking}}

\begin{cventries}
    \cventry{Department of Molecular Life Sciences, University of Zürich}{}{}{Aug22}{\begin{cvitems}
\item Introductory talk to Mass Spectrometry-based Proteomics while visiting Mark Robinson laboratory in the Department of Molecular Life Sciences, University of Zürich.
\end{cvitems}}
    \cventry{Conference: American Society of Mass Spectrometry Conference}{}{}{Jun22}{\begin{cvitems}
\item Selected talk at ASMS (American Society of Mass Spectrometry) 2022 talk on automated benchmarking. Title: Automated benchmarking enables continuous confidence in scientific software development.
\end{cvitems}}
    \cventry{Invited speaker at data science career events (Australia)}{}{}{2021-2022}{\begin{cvitems}
\item Invited speaker at the Victorian branch of the Satistical Society of Australia (SSA VIC) Industry Showcase Night (2021)
\item Invited speaker at the Women in Machine Learning and Data Science (WiMLDS) Career Transitions in ML and AI meetup in Melbourne (2021)
\item Invited speaker at the SSA VIC Early Career Panel (2022)
\end{cvitems}}
    \cventry{Invited speaker at data science career events (R-Ladies Baltimore)}{}{}{Nov21}{\begin{cvitems}
\item Panel Discussion on Careers in Data Science (Event page: \href{shorturl.at/akvDG}{shorturl.at/akvDG})
\end{cvitems}}
    \cventry{Speaker at R-Ladies Melbourne}{}{}{Aug2021}{\begin{cvitems}
\item Title: A remote glimpse into the useR! 2021 conference (Recording: \href{https://www.youtube.com/watch?v=XBoWCTYUvgY}{\faExternalLink})
\end{cvitems}}
    \cventry{Virtual Brown Bag by Eliiza}{}{}{Sep20}{\begin{cvitems}
\item Title: "Automating Data Extraction from documents" (Recording: \href{https://www.youtube.com/watch?v=pBJoYr_oLEI&t=2s}{\faExternalLink})
\end{cvitems}}
    \cventry{PhD completion seminar (WEHI)}{}{}{Aug19}{\begin{cvitems}
\item Title:Using the transcriptome to study therapy response in luekaemia (Recording: \href{https://www.youtube.com/watch?v=JiX-byutVLw&t=5s}{\faExternalLink})
\end{cvitems}}
    \cventry{Invited talk at the Monash Bioinformatics weekly seminar}{}{}{Apr18}{\begin{cvitems}
\item Title: A suite of Bioinformatics tools to call and explore somatic mutations over time from RNA-Seq (Slides: \href{shorturl.at/FHJN5}{\faExternalLink})
\end{cvitems}}
    \cventry{Speaker at R-Ladies Melbourne monthly meetup}{}{}{Feb18}{\begin{cvitems}
\item Title: Producing publication ready document in R Markdown (Slides: \href{http://rpubs.com/annaquagli/471405}{\faExternalLink})
\end{cvitems}}
    \cventry{Conference: ABACBS Selected talk}{}{}{Dec18}{\begin{cvitems}
\item Title: Correcting unwanted variation in RNA-seq data derived from a multicentre study of Leukemia (Slides \href{shorturl.at/aBFIK}{\faExternalLink})
\end{cvitems}}
    \cventry{Conference: Bioconductor Asia conference Invited Speaker}{}{}{2017/2018}{\begin{cvitems}
\item Invited talk to represent R-Ladies Melbourne (Slides: \href{shorturl.at/rKY28}{\faExternalLink})
\end{cvitems}}
    \cventry{Conference: Royal Statistical Society Selected Talk, Cardiff}{}{}{Sep18}{\begin{cvitems}
\item Short talk: "Correcting unwanted variation in RNA sequencing data from a multi-centre study of leukaemia (Slides \href{shorturl.at/dlu25}{\faExternalLink})
\end{cvitems}}
    \cventry{Conference: useR! 2018 Selected Workshop Presenter, Brisbane}{}{}{Jul18}{\begin{cvitems}
\item Looking to clean your data? Learn how to Remove Unwanted Variation with R (tutorial video \href{https://bit.ly/2DNcypO}{\faExternalLink}) and Introduction to textual analysis of social media data with R, using the idytext approach (tutorial video \href{https://bit.ly/2t0k1LH}{\faExternalLink})
\end{cvitems}}
    \cventry{Conference: COMBINE Invited instructor, Melbourne}{}{}{2017}{\begin{cvitems}
\item Workshop title: “Introdcution to Bioconductor”. Invited to prepare and lead part of the one-day workshop. Material at \href{https://github.com/COMBINE-Australia/2017-05-19-bioconductor-melbourne}{https://github.com/COMBINE-Australia/2017-05-19-bioconductor-melbourne}.
\end{cvitems}}
    \cventry{Conference: COMBINE Selected Poster and Talk}{}{}{2016}{\begin{cvitems}
\item Poster Title and Short Talk: Finding Optimal Coverage to sequence RNA (Slides: \href{shorturl.at/dlorS}{\faExternalLink})
\end{cvitems}}
\end{cventries}

\newpage

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\footnotesize

\begin{itemize}
\item
  J. Bloom; \textbf{A. Quaglieri}; A. Triantafyllidis; P. Burton Ngov;
  G. Infusini; A. Webb (2021) ``Mass Dynamics 1.0: A Streamlined,
  Web-Based Environment for Analyzing, Sharing, and Integrating
  Label-Free Data''. Journal of Proteome Research. DOI:
  10.1021/acs.jproteome.1c00683
  \href{10.1021/acs.jproteome.1c00683}{\faExternalLink}
\item
  \textbf{A. Quaglieri}; C. Flensburg; T.P Speed; Ian J Majewski (2020).
  ``Finding a suitable library size to call variants in RNA-Seq''. BMC
  Bioinformatics 21, 553. DOI:
  \url{https://doi.org/10.1186/s12859-020-03860-4}
  \href{https://doi.org/10.1186/s12859-020-03860-4}{\faExternalLink}
\item
  \textbf{Anna Quaglieri} (2019) PhD Thesis: ``Using transcriptomics to
  study relapse in acute myeloid leukaemia'', Published at University of
  Melbourne \href{shorturl.at/drABC}{\faExternalLink}
\item
  C. D. DiNardo; I. S. Tiong; \textbf{A. Quaglieri}; S. MacRaild; S.
  Loghavi; F. C. Brown; R. Thijssen; G. Pomilio; A. Ivey; J. M. Salmon
  et al.~(2020) ``Molecular Patterns of Response and Treatment Failure
  after Frontline Venetoclax Combinations in Older Patients with AML''.
  Blood 135 (11): 791-801. DOI: 10.1182/blood.2019003988
  \href{10.1182/blood.2019003988}{\faExternalLink}
\item
  TS Scerri; \textbf{A. Quaglieri}, C. Cai; J JZernant; N. Matsunami; L.
  Baird; L. Scheppke; R. Bonelli; LA Yannuzzi; M. Friedlander; MacTel
  Project Consortium; C.A. Egan; M. Fruttiger; M. Leppert; R. Allikmets;
  M. Bahlo (2017) ``Genome-wide analysis identifies common variants
  associated with macular telangiectasia type 2'' Nature Genetics
  49(4):559-567. DOI: 10.1038/ng.3799
  \href{10.1038/ng.3799}{\faExternalLink}
\item
  A. Farioli; S. Mattioli; \textbf{A. Quaglieri}; S. Curti; F.S.
  Violante; D. Coggon (2014) ``Musculoskeletal pain in Europe: the role
  of personal, occupational, and social risk factors.'' Scandinavian
  Journal of Work, Environment \& Health 40(1):36-46. DOI:
  10.5271/sjweh.3381 \href{10.5271/sjweh.3381}{\faExternalLink}
\end{itemize}

\hypertarget{public-outreach}{%
\section{Public Outreach}\label{public-outreach}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Research Video – “A genetic treasure map: new research into MacTel”}: Short Movie: https://bit.ly/2CWnu2H. This short movie tells the story of our WEHI team’s discovery of the genetic causes of MacTel published in Thomas S et al., Nature Genetics, 2017.}{}{2017\newline}
    \cvhonor{}{\textbf{R-Ladies blog posts}: Summary and learnings after being the main organiser of the group in 2018: https://r-ladiesmelbourne-team.netlify.app/ and https://rladiesmelb2018.netlify.app/.}{}{2018\newline}
\end{cvhonors}

\hypertarget{awards-and-scholarships}{%
\section{Awards and scholarships}\label{awards-and-scholarships}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Poster Prize - COMBINE Conference}: Poster title: Correcting for unwanted heterogeneity in RNA sequencing data derived from a multicentre study of leukemia.}{}{2018\newline}
    \cvhonor{}{\textbf{Travel Grants – Bioconductor Asia Conference}: Both years invited to present about R-Ladies Melbourne achievements.}{}{2016/2017\newline}
    \cvhonor{}{\textbf{Travel Grant – ABACBS Bioinformatics conference}: Presented poster short Talk: Finding Optimal Coverage to sequence RNA (Slides: shorturl.at/dlorS)}{}{2016\newline}
    \cvhonor{}{\textbf{Poster Prize and Speaker prize – ABACBS and COMBINE Conferences}: Poster and short talk title: Finding a suitable library size to call mutations from RNA Sequencing.}{}{2016\newline}
    \cvhonor{}{\textbf{AMSI Scholarship}: Winter school in Biological and Environmental Mathematical Modelling, Brisbane}{}{2016\newline}
    \cvhonor{}{\textbf{ISICO Paper Prize}: Price from the Italian Scientific Institute of the Spinal Cord – 2014 for Farioli A et al, 2014.}{}{2014\newline}
\end{cvhonors}


\label{LastPage}~
\end{document}
